Title

### 2024-05-13 paper/main.tex
Updates

	Inspired by the modification process in SEMs, in this paper, we
	introduce a data-driven modification process aimed at assisting
	researchers in manually constructing or modifying DAGs generated by an
	algorithm. The first step of this process involves identifying pairs of
	variables whose observed association is not fully explained by the
	model. The user can then make modifications to the model by adding
	edges between such variables while using their domain expertise to
	decide the direction of the edge. For the measure of association, in
	the case of continuous and discrete variables we can use effect sizes,
	however no such measure of association is present for mixed data. We
	propose a novel (conditional) measure of association for mixed data
	based on canonical correlations. We also present a graphical web-tool
	that can assist researchers in iteratively modifying and constructing
	their DAGs. We theoretically show that in the presence of an oracle,
	this iterative modification process is consistent in recovering the
	true DAG. Empirically, we show that this process performs comparably to
	PC and Hill-Climb Search algorithms if the user is able to correctly
	identify the direction of the edge in one out of three cases.
\end{abstract}

>>>>

	Inspired by the specification search in SEMs, in this paper, we
	introduce a data-driven modification process aimed at assisting
	researchers in manually constructing or modifying DAGs generated by an
	algorithm. The first step of this process involves identifying pairs of
	variables whose observed association is not fully explained by the
	model. The user can then make modifications to the model by adding
	edges between such variables while using their domain expertise to
	decide the direction of the edge. For the measure of association, in
	the case of continuous and discrete variables we can use effect sizes,
	however no such measure of association is present for mixed data. We
	propose a novel (conditional) measure of association for mixed data
	based on canonical correlations. We also present a graphical web-tool
	that can assist researchers in iteratively modifying and constructing
	their DAGs. We theoretically show that in the presence of an oracle,
	this iterative modification process is consistent in recovering the
	true DAG. Empirically, we show that this process performs comparably to
	PC and Hill-Climb Search algorithms if the user is able to correctly
	identify the direction of the edge in one out of three cases.
\end{abstract}
